%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%--------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%--------------------------------------------

\documentclass{article} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage{url}
\usepackage{color}
\usepackage{etaremune}
%\renewcommand\familydefault{\sfdefault}

\newcommand{\hot}[1]{\textcolor{red}{#1}} 

\begin{document}

\noindent
{\Large{\bf Charles Puelz}} \\

\noindent
email: \url{charles.puelz@bcm.edu} \\
website: \url{cpuelz.github.io} \\ \\
1102 Bates Street, Suite C 430.01 \\
Department of Pediatrics-Cardiology \\ 
Baylor College of Medicine \\
Texas Children's Hospital \\
Houston, TX 77030

\vspace{0.2cm}
\noindent
{\small (\url{updated:} \today)} \\

%--------------------------------------------
%	EDUCATION SECTION
%--------------------------------------------

\noindent
{\bf \large Research Interests} \\

\indent
mathematical physiology and medicine, numerical methods for partial differential equations

\vspace{0.5cm}
\noindent
{\bf \large Experience}

\vspace{0.25cm}
\indent 
{\em Assistant Professor}  \hspace*{\fill} 8/2020-present \\
\indent
Department of Pediatrics, Section of Cardiology \\
\indent Baylor College of Medicine and Texas Children's Hospital

\vspace{0.1cm}

\indent 
{\em Adjunct Assistant Professor}  \hspace*{\fill} 3/2021-present  \\
\indent
Department of Mathematics \\
\indent North Carolina State University University

\vspace{0.1cm}
\indent
{\em Lecturer} \hspace*{\fill} 7/2020-present \\
\indent
Department of Computational Applied Mathematics and Operations Research \\
\indent Rice University 

\vspace{0.1cm}
\indent
{\em Visiting Researcher} \hspace*{\fill} 8/2018-present  \\
\indent
Department of Mathematics \\
\indent University of North Carolina at Chapel Hill

\vspace{0.1cm}
\indent
{\em Assistant Professor/Courant Instructor} \hspace*{\fill} 9/2018-7/2020 \\ 
\indent Courant Institute of Mathematical Sciences \\
\indent New York University \\
\indent
advisor: Charles Peskin 

\vspace{0.1cm}
\indent
{\em Postdoctoral Researcher} \hspace*{\fill} 7/2017-8/2018 \\
\indent Department of Mathematics \\
\indent University of North Carolina at Chapel Hill \\
\indent
advisor: Boyce Griffith 

\vspace{0.1cm}
\indent 
{\em Graduate Researcher}
 \hspace*{\fill} 8/2011-5/2017 \\
\indent Department of Computational and Applied Mathematics \\ 
\indent Rice University \\
\indent 
advisors: Beatrice Riviere, Craig Rusin, Mark Embree 

\vspace{0.1cm}
\indent
{\em Undergraduate Researcher} \hspace*{\fill} Summer 2010 \\
\indent Department of Mathematics \\
\indent Massachusetts Institute of Technology  \\
\indent
advisor: Laurent Demanet 

\vspace{0.1cm}
\indent
{\em Undergraduate Researcher} \hspace*{\fill} Summer 2009 \\
\indent
Max Planck Institute for Dynamics and Self-Organization \\
\indent advisor: Tsampikos Kottos 
%\renewcommand{\arraystretch}{1.5} % Default value: 1
%\begin{tabular}{ l l }
%%{\bf Course } & {\bf Date } &  {\bf Institution} & {\bf Role} \\
%Assistant Professor of Pediatrics-Cardiology, Baylor College of Medicine & 8/2020-present \\
%Lecturer, Dept.~of Computational and Applied Math, Rice University & 7/2020-present \\
%\vtop{\hbox{\strut Assistant Professor/Courant Instructor, Courant Institute of Mathematical Sciences, NYU}\hbox{\strut advisor: Charles Peskin}} & 9/2018-7/2020 \\ 
%Visiting Researcher, Dept.~of Mathematics, University of North Carolina at Chapel Hill & 8/2018-present \\
%\vtop{\hbox{\strut Postdoctoral Researcher, Dept.~of Mathematics, University of North Carolina at Chapel Hill}\hbox{\strut advisor: Boyce Griffith}} & 7/2017-8/2018 \\
%\vtop{\hbox{\strut Graduate Researcher, Dept.~of Computational and Applied Math, Rice University}\hbox{\strut advisors: Beatrice Riviere, Craig Rusin, Mark Embree}} & 8/2011-5/2017 \\
%\vtop{\hbox{\strut Undergraduate Researcher, Dept.~of Mathematics, Massachusetts Institute of Technology}\hbox{\strut advisor: Laurent Demanet}} & Summer 2010 \\
%\vtop{\hbox{\strut Undergraduate Researcher, Max Planck Institute for Dynamics and Self-Organization}\hbox{\strut advisor: Tsampikos Kottos}} & Summer 2009 \\
%\end{tabular}

%\vspace{0.5cm}
%\noindent
%{\bf \large Experience}
%\begin{itemize}
%\item Assistant Professor/Courant Instructor, September 2018-present \\
%  Courant Institute of Mathematical Sciences, New York University \\
%  advisor: Charles Peskin
%\item Postdoctoral Research Associate, July 2017-August 2018 \\
%Visiting Researcher, August 2018-present \\
%Department of Mathematics, University of North Carolina, Chapel Hill  \\
%advisor: Boyce Griffith
%%\item Graduate Researcher, May 2014-May 2017\\
%%Department of Pediatrics-Cardiology, Baylor College of Medicine
%\item Graduate Research Assistant, August 2011-May 2017 \\
%Department of Computational and Applied Mathematics, Rice University \\
%advisors: Beatrice Riviere, Craig Rusin, Mark Embree
%\item Undergraduate Research Assistant, Summer 2010 \\
%Department of Mathematics, Massachusetts Institute of Technology  \\
%advisor: Laurent Demanet
%\item Undergraduate Research Assistant, Summer 2009 \\
%Max Planck Institute for Dynamics and Self-Organization \\
%advisor: Tsampikos Kottos
%\end{itemize}

\vspace{0.5cm}
\noindent
{\bf \large Education}
\begin{itemize}
\item Ph.D. in Computational and Applied Mathematics, Rice University, Houston, TX \hspace*{\fill} May 2017 \\
title: {\em Numerical methods and applications for reduced models of blood flow} \\
advisors: Beatrice Riviere, Craig G. Rusin  \\
committee: Matthias Heinkenschloss, Jane Grande-Allen, Sun\v{c}ica \v{C}ani\'c 
\item M.A. in Computational and Applied Mathematics, Rice University, Houston, TX \hspace*{\fill} May 2013 \\
title: {\em Improved spectral calculations for discrete Schr\"odinger operators} \\
advisor: Mark Embree \\
committee: Danny Sorensen, David Damanik
\item B.A. in Mathematics and B.A. in Physics, Wesleyan University, Middletown, CT \hspace*{\fill} May 2011 \\
Phi Beta Kappa and honors in mathematics
\end{itemize}


\vspace{0.5cm}
\noindent
{\bf \large Journal Papers}\\
{\footnotesize($\star$ by a name indicates the research began during their undergraduate studies)}
\begin{etaremune}
\item ``Predicting the effects of surgically determined parameters on exercise tolerance in Fontan patients.'' \\
  C. Kritpracha$^\star$, B. Riviere, C. Puelz. \\
  {\em submitted}, 2023.
\item ``Simulating cardiac fluid dynamics in the human heart.'' \\
  M. Davey, C. Puelz, S. Rossi, M.A. Smith, D.R. Wells, G. Sturgeon, P. Segars, J.P. Vavalle, C.S. Peskin, B.E. Griffith  \\   
{\em submitted}, 2023.
\item ``A computational study of aortic reconstruction in single ventricle patients.'' \\
A.M. Taylor-LaPole, M.J. Colebank, J. Weigand, M.S. Olufsen, C. Puelz. \\
{\em Biomechanics and Modeling in Mechanobiology}, 2022.
\item ``Semi-automated construction of patient-specific aortic valve geometries from computed tomography\\ angiography data.'' \\
D. Lior, C. Puelz, C. Edwards$^\star$, S. Molossi, B. Griffith, R. Birla, C. Rusin. \\
{\em Annals of Biomedical Engineering}, 2022.
\item ``Fluid–structure interaction model of transcatheter aortic valve replacement in a patient-specific aortic root.'' \\
J.A. Brown, J.H. Lee, M.A. Smith, D.R. Wells, A. Barrett, C. Puelz, J.P. Vavalle, B.E. Griffith. \\
{\em Annals of Biomedical Engineering}, 2022.
\item ``Optimal fenestration of the Fontan circulation.'' \\
Z. Ahmad$^\star$, L.H. Jin$^\star$, D.J. Penny, C. Rusin, C.S. Peskin, C. Puelz. \\
{\em Frontiers in Physiology - Computational Physiology and Medicine}, 13, 2022.
\item ``Simulating liquid-gas interfaces and moving contact lines with the immersed boundary method.'' \\
M.Y. Li$^\star$, D. Chin$^\star$, C. Puelz, P. Sanaei. \\
{\em Physics of Fluids}, 34(5), 2022.
\item ``Computer simulation of surgical interventions for the treatment of refractory pulmonary hypertension.'' \\
S.W. Han$^\star$, C. Puelz, C.G. Rusin, D.J. Penny, R. Coleman, C.S. Peskin. \\
{\em Mathematical Medicine and Biology}, 2022.
\item ``A reduced model for solute transport in compliant blood vessels with arbitrary axial velocity profile.'' \\
R. Masri, C. Puelz, B. Riviere. \\
{\em International Journal of Heat and Mass Transfer}, 176, 2021.
\item ``A discontinuous Galerkin method for blood flow and solute transport in one dimensional vessel networks.'' \\
R. Masri, C. Puelz, B. Riviere. \\
{\em Communications on Applied Mathematics and Computation}, 4, pp. 500-529, 2022.
\item ``Models for plasma kinetics during simultaneous \\therapeutic plasma exchange and extracorporeal membrane oxygenation.'' \\
C. Puelz, Z. Danial$^\star$, J. Marinaro, J.S. Raval, B.E. Griffith, C.S. Peskin. \\ {\em Mathematical Medicine and Biology}, 38(2), pp. 255-271, 2021. 
\item ``A physiological model of the inflammatory-thermal-pain-cardiovascular interactions \\during a endotoxin challenge.''\\
 A. Dobreva, R. Brady, K. Larripa, C. Puelz, J. Mehlsen, and M. Olufsen. \\
{\em Journal of Physiology}, 599(5), pp. 1459-1485, 2021.
\item ``Mathematical modeling of the impact of recirculation on exchange kinetics in tandem extracorporeal membrane oxygenation and therapeutic plasma exchange.'' \\ 
C. Puelz, J. Marinaro, Y.A. Park, B.E. Griffith, C.S. Peskin, J.S. Raval.\\ 
{\em Journal of Clinical Apheresis}, 36(1), pp. 6-11, 2021.

\item ``A sharp interface method for an immersed viscoelastic  solid.'' \\
C. Puelz and B.E. Griffith.\\
{\em Journal of Computational Physics}, 409, 2020. arXiv:1902.02424.
\item ``A priori error estimates of Adams-Bashforth discontinuous Galerkin methods \\for scalar nonlinear conservation laws.'' \\
C. Puelz, B. Rivi\`ere. \\
{\em Journal of Numerical Mathematics}, 26(3), pp. 151-172, 2018.
\item ``A computational study of the Fontan circulation with fenestration or hepatic vein exclusion.'' \\
C. Puelz, S. Acosta, B. Rivi\`ere,  D. Penny, K. Brady, C.G. Rusin.\\ {\em Computers in Biology and Medicine}, 89, pp. 405-418, 2017.
\item ``Cardiovascular mechanics in the early stages of pulmonary hypertension: a computational study.''\\
 S. Acosta, C. Puelz, B. Rivi\`ere,  D. Penny, K. Brady, C.G. Rusin.\\
  {\em Biomechanics and Modeling in Mechanobiology}, 16(6), pp. 2093-2112, 2017.
\item ``Convergence of IPDG for coupled time-dependent Navier-Stokes and Darcy equations.'' \\
N. Chabaane, V. Girault, C. Puelz, B. Rivi\`ere. \\
{\em Journal of Computational and Applied Mathematics}, 324, pp. 25-48, 2017.
\item ``Comparison of reduced blood flow models using Runge-Kutta discontinuous Galerkin methods.''\\
 C. Puelz, S. \v{C}ani\'c, B. Rivi\`ere, C.G. Rusin. \\
 {\em Applied Numerical Mathematics}, 115, pp. 114-141, 2017.
\item ``Numerical method of characteristics for one-dimensional blood flow.'' \\
S. Acosta, C. Puelz, B. Rivi\`ere, C.G. Rusin, D. Penny. \\
{\em Journal of Computational Physics}, 294, pp. 96-109, 2015.
\item ``Spectral approximation for quasiperiodic Jacobi operators.''\\
 C. Puelz, M. Embree, J. Fillman. \\
 {\em Integral Equations and Operator Theory}, 82(4), pp. 533-554, 2015.
\end{etaremune}

%\vspace{0.5cm}
%\noindent
%{\bf \large Working Papers}
%\begin{enumerate}
%\item ``Hyperelastic immersed boundary finite element model of the human heart.'' C. Puelz, M. Davey, M.A. Smith, S. Rossi, D. Wells, B. Griffith. 2019.
%\item ``A fluid/structure interaction model for fetal blood flow, heart mechanics, and oxygen mixing.'' C. Puelz, C.S. Peskin, C. Phoon. 2019.
%\end{enumerate}

\vspace{0.5cm}
\noindent
{\bf \large Conference Reports and Abstracts}
\begin{enumerate}
\item ``A hyperelastic immersed boundary finite element model of the human heart.'' C. Puelz, D. Wells, M. A. Smith, S. Rossi, P. Segars, G. Sturgeon and B. E. Griffith. {\em 6th International Conference on Computational and Mathematical Biomedical Engineering}, Sendai, Japan, 2019.  
\item ``Mathematical investigation of impact of recirculation in patients receiving tandem extracorporeal membrane oxygenation and therapeutic plasma exchange.'' C. Puelz, Y.A. Park, J. Marinaro, C.S. Peskin, B.E. Griffith, J.S. Raval. {\em Journal of Clinical Apheresis}: Special Issue Abstracts from the American Society for Apheresis 40th Annual Meeting 34(2), 88-89, 2019.
\item ``Immersed boundary finite element hyperelastic heart model.'' C. Puelz, M.A. Smith, S. Rossi, G. Sturgeon, P. Segars, and B. Griffith. {\em ECCM-ECFD 2018}, Glasgow, Scotland.
\end{enumerate}

\vspace{0.5cm}
\noindent
{\bf \large Theses and Technical Reports}
\begin{enumerate}
\item {\em Numerical methods and applications for reduced models of blood flow}, PhD Thesis, Rice University, 2017.
\item {\em Improved spectral calculations for discrete Schr\"odinger operators}, Masters Thesis, Rice University, 2013.
\item ``Visualizing the Pareto Surface.'' B. Hosseini, G. Liu, C. Puelz, S. Tracht, M. Smilovic. {\em IMA Preprint Series} 2401, 2012.
\end{enumerate}

\vspace{0.5cm}
\noindent
{\bf \large Funding}
\begin{itemize}
\item AMS MRC Microconference on Parameter Estimation, August 9, 2018. \$5,350.\\
co-organized with Renee Brady, Ben Randall, and Mette Olufsen.
\item National Library of Medicine training fellowship through the Gulf Coast Consortia \\ for the Quantitative Biomedical Sciences, awarded 2014, renewed 2015 and 2016.
\end{itemize}

%\vspace{0.5cm}
%\noindent
%{\bf \large Computer Skills}
%\begin{itemize}
%\item Computer Languages: {\sc Fortran}, $C$, $C^{++}$
%\item Tools: SVN, Emacs, Git, Eclipse, netbeans, {\sc Matlab}, SolidWorks
%\item Experience with: Python
%\end{itemize}

\vspace{2cm}
\noindent
{\bf \large Professional Societies}
\begin{itemize}
\item Society for Industrial and Applied Mathematics
\item American Heart Association
\end{itemize}

\vspace{0.5cm}
\noindent
{\bf \large Honors and Awards}
\begin{itemize}
\item Career Champion Award, Rice Center for Career Development, August 2022.
\item Alan Weiser Memorial Travel Award, Rice CAAM department, April 2016.
\item Honorable Mention in the National Science Foundation GRFP competition, April 2013.
\item SIAM Student Chapter Certificate of Recognition, April 2013. 
\item Rae Shortt Prize, Wesleyan math department, April 2010. 
\item Robertson Math Award, Wesleyan math department, April 2009. 
\end{itemize}

%{\bf Research Interests}
%Numerical partial differential equations, mathematical modeling, discontinuous Galerkin methods, cardiovascular mathematics, clinical decision support, biomedical informatics, spectral theory and largescale eigenvalue algorithms

%\vspace{0.5cm}
%\noindent 
%{\bf \large Professional Membership}
%\begin{itemize}
%\item SIAM, AMS
%\end{itemize}

\vspace{0.5cm}
\noindent
{\bf \large Teaching}

\vspace{0.25cm}
%\begin{center}
\begin{tabular}{ l  l  l  l  }
  %{\bf Course } & {\bf Date } &  {\bf Institution} & {\bf Role} \\
Differential Equations in Science and Engineering (undergraduate) & S 2023 & Rice & Instructor \\
Differential Equations in Science and Engineering (undergraduate) & F 2022 & Rice & Instructor \\
Differential Equations in Science and Engineering (undergraduate) & S 2022 & Rice & Instructor \\
Matrix Analysis (undergraduate) & F 2021 & Rice & Instructor \\
Differential Equations in Science and Engineering (undergraduate) & S 2021 & Rice & Instructor \\
Computational Science I (graduate) & F 2020 & Rice & Instructor \\
Linear Algebra (undergraduate) & S 2020 & NYU & Instructor \\
Numerical Analysis (undergraduate) & F 2019 & NYU & Instructor \\
Modeling and Experiments in Fluid Dynamics (graduate) & S 2019 & NYU & Teaching Assistant \\
Numerical Analysis (undergraduate) & S 2019 & NYU & Instructor \\
Modeling and Simulation in Sci., Eng, and Econ. (undergraduate) & F 2018 & NYU & Co Instructor w/ C. Peskin \\
Differential Equations in Science and Eng. (undergraduate) & S 2015 & Rice & Teaching Assistant \\
Matrix Analysis (undergraduate) & F 2014 & Rice & Teaching Assistant \\
Matrix Analysis (undergraduate) & F 2013 & Rice & Teaching Assistant \\
Matrix Analysis (undergraduate) & S 2013 & Rice & Lab Instructor \\
Intro to Engineering Computation (undergraduate)  & F 2012 & Rice & Rice Learning Assistant  \\
\end{tabular}
%\end{center}
%\begin{itemize}
%\item Lab instructor for matrix analysis lab, Rice University, Spring 2013. \\ Organized experiments for students interested in exploring linear algebra concepts within a hands-on setting.  Students enrolled in this lab while concurrently taking a sophmore/junior level linear algebra course.
%\item Rice Learning assistant (RLA), Rice University, Fall 2012. \\ Held a weekly interactive lab section for students.  We worked through Matlab implementations of concepts introduced in the lecture portion of the class.   This position included a pedagogy course which brought RLAs together for a discussion about effective pedagogical strategies for conveying course content.  
%\item Teaching Assistant, Tutor, and Grader, Wesleyan University, Spring 2008-Spring 2011.
%\end{itemize}

\vspace{0.5cm}
\noindent
{\bf \large Thesis committees}
\begin{itemize}
\item Alyssa Taylor, PhD thesis, North Carolina State University Mathematics department. \\
Topic: Modeling of reconstructed Fontan aortas.
\item Rami Masri, PhD thesis, Rice University CAAM department, April 2022. \\
Topic: Discontinuous Galerkin methods for flow and transport problems.
\item Zach Danial, Gallatin School Colloquium committee, NYU, December 2019.
\item Rami Masri, MA thesis, Rice University CAAM department. May 2019. \\
Topic: Oxygen transport in vessel network models.
\end{itemize}

\vspace{0.5cm}
\noindent
{\bf \large Mentoring}
\begin{itemize}
\item Yimo Wang, Rice engineering student. \\
January 2023-present. \\
Topic: Automation of computer aided design for cardiac models.
\item Poom Kritpracha, Rice engineering student, co-advised with Beatrice Riviere. \\
May 2022-present \\
Topic: Numerical methods and models for species transport in the human body.
\item Kristina Montez, Rice engineering student, co-advised with Dan Lior. \\
May 2022-present \\
Topic: Image segmentation and model construction for anomalous aortic origin of coronary arteries.
\item Damian Gonzalez, Rice engineering student. \\
January 2022-May 2022 \\
Topic: Control of the circulation using compartmental models.
\item Katie Bablak, Rice engineering student, co-advised with Dan Lior. \\  January 2022-May 2022 \\
Topic: Model construction of single ventricle physiology
\item Colin Edwards, intern at BCM/TCH, co-advised with Craig Rusin and Dan Lior.\\ June 2021-May 2022. \\
Topic: Image segmentation and model construction for anomalous aortic origin of coronary arteries.
\item Raniyah Nathani, IBB summer research student at Rice, co-advised with Beatrice Riviere. \\ June 2021-July 2021. \\
Topic: Compartmental circulation models and species transport.
\item Alyssa Taylor, NCSU PhD student, co-advised with Mette Olufsen.\\ Fall 2020-present. \\
Topic: Fluid/structure interaction models for reconstructed Fontan aortas. \\
Alyssa was awarded a 2021 NSF GRFP fellowship for her project.
\item Zan Ahmad, NYU undergraduate (SURE program). \\Spring-Summer 2020. \\
Topic: Models for optimal Fontan circulations. \\
Zan was named a  Wilfred L. and Ruth S.F. Peltz Research Scholar and received a Dean's Undergraduate Research Fund scholarship for this project.
\item Zach Danial, NYU undergraduate (AM-SURE program), with Charlie Peskin.\\ Summer 2019.\\
Topic: Species advection in fluid with simple and three dimensional models.
\item Lynn Jin, NYU undergraduate (SURE program, summer 2019), with Charlie Peskin. Fall 2018-Summer 2019. \\  Topic: Zero dimensional pulsatile models for the fenestrated Fontan and fetal physiologies.
\item Margaret Anne Smith, post-bachelors at UNC-CH, with Boyce Griffith. \\Fall 2017-Fall 2018. \\
Topic: Three-dimensional geometrical modeling of the adult human heart.
%\item Teaching assistant for matrix analysis and numerical PDE, Rice University, Fall 2014, Spring 2015. \\ Held weekly recitation sessions and office hours.
\end{itemize}



\vspace{0.5cm}
\noindent
{\bf \large Service}
\begin{itemize}
\item \underline{Editorial board}: {\em Frontiers in Physiology-Computational Physiology and Medicine} (Review Editor, 2020-present).
\item \underline{Journal reviewer}: {\em Numerical Methods for Partial Differential Equations}, {\em Journal of Theoretical Biology}, {\em Journal of Engineering in Medicine}, {\em Journal of Biological Systems}, {\em Biomechanics and Modeling in Mechanobiology}, {\em PLOS ONE}, {\em Computers in Biology and Medicine}, {\em SIAM Journal on Applied Mathematics}, {\em Annals of Biomedical Engineering}, {\em Journal of Fluid Mechanics}, {\em Flow}, {\em International Journal for Numerical Methods in Biomedical Engineering}
\item \underline{Conferences/workshops}:
\begin{itemize}
\item Co-organizer for minisymposium titled ``Mathematics and Computation in Biomedicine,'' SIAM TX/LA meeting, November 2022.
\item Co-organizer for minisymposium titled ``Mathematics and Computation in Biomedicine,'' SIAM TX/LA meeting, November 2021.
\item Co-organizer for minisymposium titled ``Progress in forward and inverse problems in cardiovascular dynamics,'' SIAM CSE, March 2021.
\item Organizer for minisymposium titled ``Numerical methods and applications for cardiovascular mechanics,'' 3rd Annual Meeting of the
SIAM Texas-Louisiana Section, October 2020. 
\item Session chair for contributed presentation session titled ``Applications in CSE,'' SIAM CSE, 2019.
\item Co-organizer of AMS microconference on parameter estimation in physiological models.  August 9, 2018.
\item Co-organizer of minisymposium at the 42nd SIAM Southeastern Atlantic Section Conference titled ``Cardiovascular Modeling and Simulation.'' March 9-11, 2018. 
\item Co-organizer of an AMS minisymposium at the Joint Mathematics Meeting. Minisymposium titled ``Mathematics in Physiology and Medicine.'' January 5, 2017.
\end{itemize}
\item \underline{At New York University}:
\begin{itemize}
\item Proud-to-be-first advocate at NYU.  This is part of a program to support first generation college students.\item Co-coordinator of the applied math summer undergraduate research experience (AM-SURE) at Courant, NYU, summer 2019.
\item Co-organizer of Applied Math/Applied Math Lab seminar in the Courant Institute, 2018-2019.
\end{itemize}
\item \underline{At University of North Carolina, Chapel Hill}:
\begin{itemize}
\item Co-organizer of the Applied Mathematics Colloquium in the UNC-CH Mathematics Department, 2017-2018.
\end{itemize}
\item \underline{At Rice University}:
\begin{itemize}
\item Poster judge for 2021 IBB Summer Research Symposium, August 2021.
\item Speaker at ``Rice Summer Math Days,'' a summer program for high school students interested in studying mathematics, June 2015.
\item SIAM student chapter president, Rice University, 2012-2013.
\end{itemize}
\item \underline{Other}:
\begin{itemize}
\item Science fair judge.  Immaculate Conception School, New York City. January 29, 2020.
\end{itemize}
\end{itemize}

\vspace{0.5cm}
\noindent
{\bf \large Presentations}
\begin{enumerate}
\item ``Computer modeling in cardiology: from zero-dimensional to three-dimensional approaches'' \\
Food and Drug Administration Modeling and Simulation Working Group, April 6, 2023.
\item ``Fluid-structure interaction models for blood flow in the human circulation.'' \\
AMS Spring Southeastern Section Meeting, Georgia Tech, March 18, 2023.
\item ``3D Physics-based modeling of AAOCA: Towards Risk Stratification \\ Through High-Performance Computation.'' \\
Texas Children's 5th Symposium on Coronary Artery Anomalies, December 1, 2022.
\item ``Computer modeling and simulation of blood flow and tissue deformation in congenital heart defects.''\\
5th Annual Meeting of the SIAM Texas-Louisiana Section, November 6, 2022.
\item ``Learning from Data: From Machine to Bedside'' (with Craig Rusin and Sebastian Acosta). \\
Texas Children's Heart Center Invited Lecture Series, May 27, 2022.
\item ``Computer simulations for pediatric and adult cardiovascular mechanics.'' \\
Baylor University Mechanical Engineering Seminar, April 11, 2022.
\item ``Immersed boundary methods for pediatric and adult cardiovascular models.''\\
4th Annual Meeting of the SIAM Texas-Louisiana Section, November 5, 2021.
\item ``A fluid/structure interaction model of the human heart.'' \\
Society for Mathematical Biology Annual Meeting.  June 17, 2021.
\item ``Simulation of a toroidal heart using a sharp interface immersed boundary method.'' \\
SIAM CSE 2021, (virtual), March 3, 2021.
\item ``Fluid-structure interaction models for describing the physiology of human hearts.'' \\ New Jersey Institute of Technology Fluids and Waves Seminar (online), November 9, 2020.
\item ``A fluid-structure interaction model of the human heart.'' \\ 3rd Annual Meeting of the SIAM Texas-Louisiana Section (online), October 18, 2020.
\item ``Fluid-structure interaction model of the human heart.'' \\
Modelling the Cardiac Function: Theory, Numerical Methods, Clinical Application (online), September 2, 2020.
\item ``A sharp interface version of the immersed boundary finite element method.'' \\
Modeling and Simulation Group Seminar (online), Courant Institute, April 23, 2020.
\item ``Computer models and numerical methods for mathematical cardiology.'' \\
Mathematics Department Special Seminar, North Carolina State University, January 21, 2020.
\item ``Computer models and numerical methods for mathematical physiology.'' \\
Mathematics Department Colloquium, Baylor University, Waco, TX, December 10, 2019.
\item ``Computer models and numerical methods for mathematical physiology.'' \\
Modeling and Simulation Group Seminar, Courant Institute, December 5, 2019.
\item ``Computer model of the human heart.'' \\
15th U.S. National Congress on Computational Mechanics, Austin, TX, July 29, 2019. 
\item ``Models for fetal heart mechanics.'' \\
joint with Lynn Jin (NYU undergrad) \\
unSURE Summer Research Seminar, Courant Institute, July 2019.
\item ``A hyperelastic immersed boundary finite element model of the human heart.'' \\
6th International Conference on Computational and Mathematical Biomedical Engineering,\\ Sendai City, Japan, June 10, 2019.
\item ``Modeling recirculation in tandem ECMO and therapeutic plasma exchange.'' \\
American Society for Apheresis annual meeting, Portland, OR, May 17, 2019.
\item ``A review of Taylor's 1953 paper on dispersion of a solute in fluid and related applications.'' \\
joint with Ondrej Maxian (Courant). \\
Modeling and Simulation Group Seminar, Courant Institute, March 2019.
\item ``Hyperelastic immersed boundary finite element model of the human heart.'' \\
SIAM CSE, Spokane, WA, 2019.
\item ``A sharp interface method for an immersed viscoelastic solid.'' \\
WONAPDE 2019, Universidad de Concepci\'on, Concepci\'on, Chile, January 23, 2019.
\item ``Hyperelastic immersed boundary finite element model of a human heart.'' \\
WONAPDE 2019, Universidad de Concepci\'on, Concepci\'on, Chile, January 23, 2019.
\item ``Computer model of the human heart.'' \\
CAAM Graduate Seminar, Rice University, Houston, TX, January 16, 2019.
\item ``Computer modeling of the human heart.'' \\
Courant Instructor Day, Courant Institute, New York, NY, October 12, 2018.
\item ``A one-dimensional vessel network model for the Fontan circulation.'' \\Biomath/Comp. Biology Colloquium, Courant Institute, New York, NY, October 2, 2018.
\item ``Construction of a hyperelastic immersed boundary model of the human heart.'' \\Biomath/Comp. Biology Colloquium, Courant Institute, New York, NY, September 18, 2018.
\item ``A hyperelastic immersed boundary model of the human heart.''\\ SIAM Life Sciences, Minneapolis, MN, 2018.
\item ``Reduced model for the Fontan circulation.''\\ SIAM Life Sciences, Minneapolis, MN, 2018.
\item ``Immersed boundary finite element hyperelastic heart model.'' \\
ECCM-ECFD, Glasgow, UK, June 2018.
\item ``Computational modeling of Fontan hemodynamics'' \\
North Carolina State University Biomathematics Seminar, Raleigh, NC, April 2018.
\item ``Discretizations of 1D blood flow models and an application to the Fontan physiology'' \\
Virginia Tech Numerical Analysis Seminar, Blacksburg, VA, November 1, 2017.
\item ``One dimensional vessel network models for studying abnormal physiologies'' \\
UNC Department of Mathematics Applied Mathematics Colloquium, Chapel Hill, NC, September 2017.
\item ``Numerical methods for blood flow'' \\
Rice CAAM department graduate colloquium, Houston, TX, March 2017.
\item ``Reduced models for blood flow'' \\
Finite Element Rodeo, University of Houston, Houston, TX, March 2017.
\item ``One-dimensional blood flow models: analysis and applications'' \\
SIAM Life Sciences, Boston, MA, July 2016.
\item ``Discontinuous Galerkin discretizations of one-dimensional blood flow models'' \\ 
Finite Element Rodeo, Texas A\&M University, College Station, TX, March 2016.
\item ``Numerical methods for reduced blood flow models'' \\
National Institute of Standards and Technology, Gaithersburg, MD, June 2015.
\item ``Discontinuous Galerkin methods for reduced blood flow models'' \\
Finite Element Rodeo, Southern Methodist University, Dallas, TX, May 2015.
\item ``An $O(N^2)$ eigenvalue algorithm for period-$N$ Jacobi operators'' \\
Joint Mathematics Meeting, San Antonio, TX, January 2015. 
\item ``Spectra of Schr\"odinger operators via transfer matrices'' \\
Rice CAAM department graduate colloquium, Houston, TX, January 2014.
\item ``Electrical networks and Polya's theorem'' \\
Rice CAAM department graduate colloquium, Houston, TX, January 2012.
\item ``Random walks and electrical networks'' \\
Wesleyan math department senior honors presentation, Wesleyan University, Middletown, CT, April 2011.
\item ``Oil drilling and mathematics'' \\ 
Wesleyan math department undergraduate colloquium, Middletown, CT, February 2011.
\end{enumerate}

\vspace{0.5cm}
\noindent
{\bf \large Posters}
\begin{enumerate}
\item ``High fidelity computer models for cardiac fluid and solid mechanics.''\\
with Margaret Anne Smith, Simone Rossi, Marshall Davey, David Wells, and Boyce Griffith. \\
BCM Cardiovascular Research Institute 8th Annual Symposium, April 2021.
\item ``A modeling study of palliations used for refractory pulmonary hypertension.'' \\
with Seong Woo Han, Craig Rusin, Dan Penny, Ryan Coleman, and Charles Peskin. \\
14th International Symposium on Neonatal and Childhood Pulmonary Vascular Disease Conference, virtual, March 2021.
\item ``Heart Modeling with the Immersed Boundary Finite Element Method.'' \\
with Margaret Anne Smith, Simone Rossi, and Boyce Griffith. \\
SIAM Annual Meeting, Portland, OR, July 2018. 
\item ``Hyperelastic immersed boundary finite element heart model.'' \\
with Margaret Anne Smith, Simone Rossi, and Boyce Griffith. \\
42nd SIAM Southeastern Atlantic Section Conference, University of North Carolina, Chapel Hill, NC, March 2018.
\item ``One-dimensional model of blood flow discretized with Runge-Kutta discontinuous Galerkin methods'' \\
SIAM Life Sciences, Boston, MA, July 2016.
\item ``Computational modeling of hypoplastic left heart syndrome for improved decision support''\\
NLM Informatics Training Conference, Ohio State University, Columbus, OH, June 2016.
\item ``Mathematical modeling of congenital heart defects and abnormal hemodynamic physiologies'' \\
Sigma Xi (Rice and TMC chapter) holiday event, Houston, TX, December 2015.
\item ``Blood flow model for improved decision support'' \\
AMIA Annual Symposium, San Francisco, CA, November 2015 
\item ``A closed-loop reduced hemodynamic model for the simulation of blood flow in patients with hypoplastic left heart syndrome'' \\
25th Keck Annual Research Conference, Bioscience Research Collaborative, Houston, TX,  October 2015.
\item ``Discontinuous Galerkin methods for reduced blood flow models'' \\
Advanced Numerical Methods in the Mathematical Sciences conference, Texas A\&M University, College Station, TX, May 2015.
\item ``Numerical methods for one-dimensional blood flow'' \\
poster at the Keck Annual Research Conference, Bioscience Research Collaborative, Houston, TX, November 2014. 
\end{enumerate}

\vspace{0.5cm}
\noindent
{\bf \large Conferences and Workshops}
\begin{itemize}
\item 2023 AMS Spring Southeastern Sectional Meeting, Georgia Tech, March 18-19, 2023.
\item 5th Annual Meeting of the SIAM Texas-Louisiana Section, November 4-6, 2022.
\item Aligning Expectations: Optimizing Mentoring Relationships, BCM Office of Faculty Affairs and Faculty Development, October 18, 2022.
\item 4th Annual Meeting of the SIAM Texas-Louisiana Section, November 5-7, 2021. 
\item Society for Mathematical Biology Annual Meeting, June 13-17, 2021.
\item 14th International Symposium on Neonatal and Childhood Pulmonary Vascular Disease Conference, March 3-5, 2021
\item SIAM Computational Science and Engineering, March 1-5, 2021.
\item 3rd Annual Meeting of the SIAM Texas-Louisiana Section, October 16-18, 2020. 
\item Modelling the Cardiac Function: Theory, Numerical Methods, Clinical Applications, August 31 - September 2, 2020.
\item 15th U.S. National Congress on Computational Mechanics, Austin, TX, July 28-August 1, 2019.
\item 6th International Conference on Computational and Mathematical Biomedical Engineering,\\ Sendai City, Japan, June 10-12, 2019.
\item American Society for Apheresis annual meeting, Portland, OR, May 14-18, 2019.
\item SIAM CSE, Spokane, WA, February 25-March 1, 2019.
\item Sixth Chilean Workshop on Numerical Analysis of Partial Differential Equations (WONAPDE), Concepci\'on, Chile, January 21-25, 2019.
\item SIAM Life Sciences, Minneapolis, MN, August 6-9, 2018.
\item SIAM Annual Meeting, Portland, OR, July 9-13, 2018.
\item European Conference on Computational Mechanics/European Conference on Fluid Dynamics (ECCM-ECFD), Glasgow, UK, June 11-15, 2018.
\item 42nd SIAM Southeastern Atlantic Section Conference, University of North Carolina, Chapel Hilll, NC, March 9-11, 2018.
\item Finite Element Rodeo, University of Houston, Houston, TX, March 3-4, 2017.
\item Joint Mathematics Meeting, Atlanta, GA, January 4-7, 2017.
\item SIAM Life Sciences, Boston, MA, July 11-14, 2016.
\item National Library of Medicine Informatics Training Conference, Ohio State University, Columbus, OH, June 27-28, 2016.
\item AMS MRC: Mathematics in Physiology and Medicine, Snowbird Resort, Snowbird, UT, June 19-25, 2016.
\item Finite Element Rodeo, Texas A\&M University, College Station, TX, March 4-5, 2016.
\item AMIA Annual Symposium, San Francisco, CA, November 14-18, 2015.
\item 25th Keck Annual Research Conference, Bioscience Research Collaborative, Houston, TX, October 15-16, 2015.
\item National Library of Medicine Informatics Training Conference, National Institutes of Health, Bethesda, MD, June 23-24, 2015.
\item Advanced Numerical Methods in the Mathematical Sciences, Texas A\&M University, College Station, TX, May 4-7, 2015.
\item Finite Element Rodeo, Southern Methodist University, Dallas, TX,
 February 27-28, 2015.
\item Joint Mathematics Meeting, San Antonio, TX, January 10-13, 2015. 
\item National Library of Medicine Informatics Training Conference, University of Pittsburgh, Pittsburgh, PA, June 17-18, 2014.
\item 24th Keck Annual Research Conference, Bioscience Research Collaborative, Houston, TX, November 7, 2014.
\item Gene Golub SIAM Summer School on Numerical Linear Algebra, Fudan University, Shanghai, China, July 22-August 9, 2013.
\item Recent Advances in Harmonic Analysis and Spectral Theory, Texas A\&M University, College Station, TX, August 6-10, 2012.
\item Mathematical Modeling in Industry XVI, University of Calgary, Calgary, Alberta, July 18-27, 2012.
\end{itemize}



%--------------------------------------------
%	EXAMPLE SECTION
%--------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%--------------------------------------------

\end{document}
